Explore anomalies

### 2017-11-21 analysis/evi/explore_anomalies.Rmd
include new analysis evi anomalies

>>>>

```{r percentage_greening}

per_sa <- per_sa %>% add_row(clu_pop2 = 'Northern slope',
                             type = 'greening',
                             count_clu = 0, per = 0.00, y = 2005)

per_pixels_green <- per_sa %>% 
  ggplot(aes(x=type, y=per, fill=as.factor(y))) + geom_bar(stat='identity', position = "dodge") + facet_wrap(~clu_pop2) + 
  theme_bw() + 
  theme(strip.background = element_rect(colour = "black", fill = "white"))

per_pixels_green 
pdf(file=paste0(di, "/out/anomalies/evi/per_pixels_green.pdf"), height = 6, width =10)
traj_plot_popsa
dev.off()
